A Multi-Satellite Investigation of the US Corn Belt in the Period 2010-2016 with a Focus on Solar-Induced Fluorescence

### 2019-04-23 manuscript/manuscript.tex
Updates

A crucial step in the SIF retrieval process is the bias correction. Small non-linearities in the analogue-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values. In order to rid the measurements of these instrument artefacts, the retrieved SIF values need to be corrected. To achieve the bias correction, we use a slightly different method compared to \citet{Frankenberg2011}. First, we use the ESA CCI Land Cover map v2.0.7 \citep{Bontemps2013} to obtain the land cover classes for the surfaces seen by each GOSAT measurement (see Section~\ref{sec:collocation}). To identify footprints which can be assumed to be permanently free of vegetation, we consider only surfaces where at least $95\%$ of all land cover-class pixels within the footprint belong to the types: urban, desert, snow and ice, or any bare type. This approach has the advantage that highly reflective surfaces like ice shields or deserts are used for the correction process, and also darker surfaces such as mountainous regions.

@@

\begin{figure}[htbp]
\centering
\includegraphics{../coverage_map.png}
\caption{Land cover classes (left) and GOSAT sampling density (right) shown for the region of interest ($104$W - $87.5$W, $37$N - $49$N). Yellow land cover pixels correspond to crop, orange represents grassland, green-colored pixels are various tree types, and red areas are urban regions. In the right picture, all GOSAT soundings for the entire time period $2010-2016$ are collected and visualized as a density map to illustrate the both sparse and irregular sampling pattern.}
\label{fig:sampling}
\end{figure}

@@

Repeating the same analysis on a monthly basis, a different picture than Figure~\ref{fig:lc_coverage} can arise, as GOSAT's sampling is not only non-uniform geographically, but also changed over time. In Figure~\ref{fig:lc_diff_monthly}, the differences between GOSAT-seen and total ROI land cover class coverage for monthly aggregates is shown for the three most prevalent classes. We observe that differences can change somewhat drastically, and for certain months even reach $10\%$. Months in which the differences are fairly large for cropland and grassland LC types are: $2013/04$, $2014/02$, $2014/03$, $2014/04$, $2014/11$, $2015/02$ and $2015/04$, $2016/08$. Due to the careful handling of the EO data set sampling, the difference in LC coverage should not have a significant impact on the further analysis and results. It is also important to note that while Figures~\ref{fig:lc_coverage} and \ref{fig:lc_diff_monthly} confirm that the LC classes are more or less well-represented, vegetation responses can vary geographically over the Corn Belt, even though they might share the same LC classification.

As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ any cropland-type surface were kept for the subsequent analysis.

@@

The SIF retrievals are aggregated on a monthly basis, where the mean of all measurements inside the ROI for a given month are considered. As we have two different polarizations (P, S) and three different calibration procedures (seasonal, annual, spline-based), there are a total of six SIF time series. Figure~\ref{fig:sif_ts} shows this ensemble of SIF data, where the thick line is the median of all six time series. The bottom panel shows the anomalies, and the shaded area visualizes the respective minimum and maximum value of the given month to show the spread of the ROI-averaged SIF. We find that the variability in the six SIF time series stems mostly from the two different polarizations, rather than the calibration methodology. Months with less than $100$ measurements are dropped from both the visualization and the analysis, which affects only December $2012$ and January $2015$, months in which GOSAT was only partially operative due to instrumental issues.

\begin{figure}[htbp]
\centering
\includegraphics{../SIF_overview.pdf}
\caption{The SIF time series (top panel) and corresponding anomaly plot (bottom panel). In the top panel, the green line represents the median of the six monthly-averaged SIF time series (two polarization states, three bias correction schemes), while the blue-dashed line represents the measurement count per month. The dotted lines in the bottom plot mark the $2\sigma$ and $3\sigma$ values of the anomalies.}
\label{fig:sif_ts}
\end{figure}

The anomalies in Figure~\ref{fig:sif_ts} (bottom) are calculated as the difference between the current month and the median of all of the same months over the seven-year period. While the time series itself does not immediately reveal any striking features, the anomalies show several important ones. Given this relatively short period of seven years, only one month shows an anomalous value beyond $3\sigma$ (five months beyond $2\sigma$). We conclude that this short time period does not have a strong baseline, as most years have one ore more anomalous months. [REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every year and potential anomaly within the context of other climatological and agricultural drivers. In chronological order, they can be easily identified and related to known meteorological events.

@@

In $2011$, we see a small negative anomaly for spring, despite average precipitation and temperatures for that season. The reason for the negative anomaly is hinted at by the positive GRACE anomaly for $2011$ (Fig.~\ref{fig:anomalies_0} top row). Large amounts of melting snow in the northern Corn Belt, as well as high precipitation in the south eastern corner (Missouri) have caused massive flooding of the Mississippi and Missouri rivers. As most parts of the ROI have not seen any increased rainfall, the precipitation anomaly plot in Figure~\ref{fig:anomalies_0} (second row) does not show any significant outlier. The flooded areas, however, are visible as a positive anomaly in the GRACE data. While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts} (maybe need better / more references to this), regions like Iowa, Nebraska and Kansas were not as severely impacted, hence the smaller anomaly.

@@

In $2013$ and $2014$, we again see a negative anomaly for spring and early summer. For these two years, the anomalies have similar causes. In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days - as well as caused slow maturing of crops.

@@

%\begin{figure}[htbp]
%\centering
%\includegraphics{../anomalies_755_abs_1_median.pdf}
%\caption{default}
%\label{fig:anomalies_1}
%\end{figure}

@@

We compare gross flux anomalies from CASA, as well as net flux anomalies obtained through the inversion of GOSAT XCO$_2$ measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies. Figure~\ref{fig:anomalies_3} shows that the large drought event of 2012 is represented in both gross and net fluxes - several other anomalies (2010, 2011, 2015) are also well-represented in both flux data.

\begin{figure}[htbp]
\centering
\includegraphics{../anomalies_755_abs_2_median.pdf}
\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [W/m$^2$/sr/$\mu$m].}
\label{fig:anomalies_3}
\end{figure}

@@

The US Corn Belt is a very specific type of biome. As recently investigated by \citet{Alter2017}, it even generates its own climate, with the agricultural intensification resulting in cooler temperatures and increased rainfall. Despite the ROI being almost $1800 \times 10^9\;\mathrm{m}^2$ ($\approx 440$ million acres) in area, around half of it is irrigated cropland. Meteorological conditions are thus not the only factor in determining the vegetation onset and productivity of one given season. It was pointed out in Section~\ref{sec:SIF_TS} that for certain years, the rainfall amount in springtime have caused delays in the planting of crops. To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports \citep{USDA2010,USDA2011,USDA2012,USDA2013,USDA2014,USDA2015,USDA2016}. In these reports, the percentage of acreage planted is recorded based on farmer surveys. We translate these weekly state-wide data for the whole ROI by multiplying with the total planted area for that given year and state in order to obtain an effective "planted area". We compare this number for every year against the integrated (or cumulative) SIF radiances (monthly ROI averages) from February onwards to June.

\begin{figure}[htbp]
\centering
\includegraphics{../corn_soy_planted_sif.pdf}
\caption{Crop planting progress (1 acre $\approx 4047$ m$^2$) at week 18 as a function of time-integrated monthly SIF radiances from February to June. Uncertainty bars for SIF is the standard error on the 6 different SIF time series. Low values for the years $2013$ and $2014$ are the result of planting delays due to rainfall and cold temperatures (see Section \ref{sec:SIF_TS}).}
\label{fig:corn_soy_planted_sif}
\end{figure}

The result for both corn and soybeans is shown in Figure~\ref{fig:corn_soy_planted_sif}. It shows that the time-integrated SIF radiances correspond very well to the crop planting progress of that given year at the first week of May (week 18). [TODO: If I change the months / weeks slightly - the result improves a bit; justification?]

The SIF radiances do not only reflect the crop status during the growing season. Also the total corn and soybean yield for the entire year has an apparent linear relationship with the integrated SIF radiances from June until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}. The record-low yield due to the 2012 drought is highly apparent in the figure, also making it clear that a yield prognosis based on planting progress alone (Fig.~\ref{fig:corn_soy_planted_sif}) is not feasible.

\begin{figure}[htbp]
\centering
\includegraphics{../corn_soy_yield_sif.pdf}
\caption{Annual crop yield (1 bushel corn $\approx 25.4$ kg, 1 bushel soybean $\approx 27.2$ kg) from June to October as a function of the time-integrated monthly SIF radiances from June to October. The uncertainty bars for crop yield is the standard error of all nine states within the ROI, however that number is not taken into account for the linear regression. The value in the bracket within the regression equation is the uncertainty of the fitted slope and offset.}
\label{fig:corn_soy_yield_sif}
\end{figure}

The observed good relationship between SIF, and crop planting and crop yield is not particularly surprising, given the good correlation between SIF and NDVI/EVI time series anomalies ($r > 0.6$, not pictured). The predictive power of hyperspectral indices from remote sensing instruments in characterising crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010} and \citet{Mkhabela2011}. Even in the case of the entire Corn Belt, NDVI/EVI remain better predictors than SIF for both planting ($r = 0.88$ / $r = 0.86$ for corn) and yield ($r = 0.98$ / $r = 0.96$ for corn). Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.92$ and $r = 0.90$ for corn planting, and $r = 0.98$ and $r = 0.98$ for corn yield. The better performance of NDVI/EVI as well as LAI and FVC most likely stem from the noisy nature of the SIF data (see Section \ref{sec:GOSAT_SIF}). Even at the scale of the ROI, monthly values of the ROI-averaged SIF can have an attached uncertainty of at least $\approx 20\%$ (estimated through sub-regional aggregation).

@@

The first control is to look at the relationship between total planted area in the nine states against crop yield, where the planted area and yield values are separate for each crop. We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative and weak correlation ($r = 0.27$). This negative correlation for corn is solely due to the year 2012, removing that one data point reduces the correlation coefficient to $r = 0.00$, which is already hinted by the large p-value of $0.23$. The positive and significant correlation for soybeans is explained through both the steadily increasing yields together with a general increase in soybean planting. The USDA projects soybeans to reach similar levels to corn in terms of amount of planted acres in the near future \citep{USDA-prognosis}. We cannot distinguish whether a specific GOSAT footprint covered a soy field or a corn field (or any other crop) at the time of measurement. Hence we can not completely reject the possibility that the SIF signal we see in Figure~\ref{fig:corn_soy_yield_sif} is due to mainly covering soybean fields. Since most farmers in the Corn Belt practice individual crop rotation between corn and soybeans \citep{suyker2012gross}, it is most likely that we are sampling a mix between corn, soybeans, and to a lesser extent, wheat. We therefore assume that the SIF-yield relationship is not driven due to sampling that is heavily weighted towards soybean fields.

@@

For the third control, we investigate a potential sampling bias. Already shown in Figure~\ref{fig:lc_diff_monthly}, there is a variability in terms of the surfaces sampled by GOSAT, mostly a result of changing cloud cover and sampling strategy. We compare the crop yield to the fraction of cropland (as determined by the ESA CCI LC map) that all GOSAT soundings see in a given year. Here we use the same set of soundings that was pre-filtered beforehand, so only individual soundings are considered that cover more than $50\%$ of the crop type land cover type. The observed correlation at $r < 0.46$ is weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.75$), and neither relationship is statistically significant ($p > 0.15$).

@@

>>>>

A crucial step in the SIF retrieval process is the bias correction. Small non-linearities in the analogue-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values. In order to rid the measurements of these instrument artefacts, the retrieved SIF values need to be corrected. To achieve the bias correction, we use a slightly different method compared to \citet{Frankenberg2011}. First, we use the ESA CCI Land Cover map v2.0.7 \citep{Bontemps2013} to obtain the land cover classes for the surfaces seen by each GOSAT measurement (see Section~\ref{sec:collocation}). To identify footprints which can be assumed to be permanently free of vegetation, we consider only surfaces where at least $95\%$ of all land cover-class pixels within the footprint belong to the types: urban, desert, snow and ice, or any bare type. This approach has the advantage that highly reflective surfaces like ice shields or deserts are used for the correction process, as well as darker surfaces such as mountainous regions.

@@

\begin{figure}[htbp]
\centering
\includegraphics{../coverage_map.png}
\caption{Land cover classes (left) and GOSAT sampling density (right) shown for the region of interest ($104$W - $87.5$W, $37$N - $49$N). Yellow land cover pixels correspond to crop, orange represents grassland, green-colored pixels are various tree types, and red areas are urban regions. In the right picture, all GOSAT soundings for the entire time period $2010-2016$ are collected and visualized as a density map (red indicates higher sounding density) to illustrate the both sparse and irregular sampling pattern.}
\label{fig:sampling}
\end{figure}

@@

Repeating the same analysis on a monthly basis, a different picture than Figure~\ref{fig:lc_coverage} can arise, as GOSAT's sampling is not only non-uniform geographically, but also changes over time. In Figure~\ref{fig:lc_diff_monthly}, the differences between GOSAT-seen and total ROI land cover class coverage for monthly aggregates is shown for the three most prevalent classes. We observe that differences can change somewhat drastically, and for certain months even reach $10\%$. Months in which the differences are fairly large for cropland and grassland LC types are: $2013/04$, $2014/02$, $2014/03$, $2014/04$, $2014/11$, $2015/02$ and $2015/04$, $2016/08$. Due to the careful handling of the EO data set sampling, the difference in LC coverage should not have a significant impact on the further analysis and results. It is also important to note that while Figures~\ref{fig:lc_coverage} and \ref{fig:lc_diff_monthly} confirm that the LC classes are more or less well-represented, vegetation responses can vary geographically over the Corn Belt, even though they might share the same LC classification.

As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ any cropland-type surface were kept for the subsequent analysis, and we use the SIF retrievals at $755$ nm.

@@

The SIF retrievals are aggregated on a monthly basis, where the mean of all measurements inside the ROI for a given month are considered. As we have two different polarizations (P, S) and three different calibration procedures (seasonal, annual, spline-based), there are a total of six SIF time series. Figure~\ref{fig:sif_ts} shows this ensemble of SIF data, where the thick line is the median of all six time series. The bottom panel shows the anomalies, and the shaded area visualizes the respective minimum and maximum value of the given month to show the spread of the ROI-averaged SIF. We find that the variability in the six SIF time series is mostly from the two different polarizations, rather than the calibration methodologies. Months with less than $100$ measurements are dropped from both the visualization and the analysis, which affects only December $2012$ and January $2015$ when GOSAT was only partially operative due to instrumental issues.

\begin{figure}[htbp]
\centering
\includegraphics{../SIF_overview.pdf}
\caption{The SIF time series (top panel) and corresponding anomaly plot (bottom panel). In the top panel, the green line represents the median of the six monthly-averaged SIF time series (two polarization states, three bias correction schemes), while the blue-dashed line represents the measurement count per month. The dotted lines in the bottom plot mark the $\pm 2\sigma$ and $\pm 3\sigma$ values of the anomalies, and the shaded area is bounded by the lowest and largest value of the six SIF time series.}
\label{fig:sif_ts}
\end{figure}

The anomalies in Figure~\ref{fig:sif_ts} (bottom) are calculated as the difference between the current month and the median of all of the same months over the seven-year period. While the time series itself does not immediately reveal any striking features, the anomalies show several important ones. Given this relatively short period of seven years, only one month shows an anomalous value beyond $3\sigma$ (five months beyond $2\sigma$). We conclude that this short time period does not have a clear baseline, and using a simple threshold based on the standard deviation, will result in either too few or too many anomalies. We point to two studies by \citet{sun2015drought} and \citet{wolf2016warm}, which both analyze drought events with respect to a similarly short baseline. \citet{sun2015drought} investigate the 2011 drought over Texas and the 2012 drought over most parts of the central US respectively, through SIF retrieved from GOME-2 in the 2007-2013 time period.

[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore important to look at every year and potential anomaly within the context of other climatological and agricultural drivers. In chronological order, the major anomalies can be easily identified and related to known meteorological events.

@@

In $2011$, we see a small negative anomaly for spring, despite average precipitation and temperatures for that season. The reason for the negative anomaly is hinted at by the positive GRACE anomaly for $2011$ (Fig.~\ref{fig:anomalies_0} top row). Large amounts of melting snow in the northern Corn Belt, as well as high precipitation in the south eastern corner (Missouri) have caused massive flooding of the Mississippi and Missouri rivers. As most parts of the ROI have not seen any increased rainfall, the precipitation anomaly plot in Figure~\ref{fig:anomalies_0} (second row) does not show any significant outlier. The flooded areas, however, are visible as a positive anomaly in the GRACE data. While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts}, regions like Iowa, Nebraska and Kansas were not as severely impacted, hence the smaller anomaly.

@@

In $2013$ and $2014$, we again see a negative anomaly for spring and early summer. For these two years, the anomalies have similar causes. In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days - as well as caused slow maturing of crops. The delayed planting is evident in the USDA surveys and displayed Figure~\ref{fig:corn_soy_planted_sif} (next section), which shows that the planting progress by calendar week 18 was the worst in the years $2013$ and $2014$.

@@

@@

We compare gross (GPP) and net flux (NPP) 
anomalies from the Carnegie-Ames-Stanford-Approach (CASA) model, as well as net flux anomalies obtained through the inversion of GOSAT XCO$_2$ measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies. Figure~\ref{fig:anomalies_3} shows that the large drought event of 2012 is represented in both gross and net fluxes - several other anomalies (2010, 2011, 2015) are also well-represented in both model fluxes, and the fluxes obtained through inversions. The surface fluxes anomalies here are also sampled at the GOSAT measurement locations. QUESTION: Is it legit to sample surface fluxes at GOSAT locations, or do I need the full ROI?

\begin{figure}[htbp]
\centering
\includegraphics{../anomalies_755_abs_2_median.pdf}
\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [mW/m$^2$/sr/nm].}
\label{fig:anomalies_3}
\end{figure}

@@

The US Corn Belt is a very specific type of biome. As recently investigated by \citet{Alter2017}, it even generates its own climate, with the agricultural intensification resulting in cooler temperatures and increased rainfall. Despite the ROI being almost $1800 \times 10^9\;\mathrm{m}^2$ ($\approx 440$ million acres) in area, around half of it is irrigated cropland. Meteorological conditions are thus not the only factor in determining the vegetation onset and productivity of one given season. It was pointed out in Section~\ref{sec:SIF_TS} that for certain years, the springtime rainfall has caused delays in the planting of crops. To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports \citep{USDA2010,USDA2011,USDA2012,USDA2013,USDA2014,USDA2015,USDA2016}. In these reports, the percentage of acreage planted is recorded based on farmer surveys. We translate these weekly state-wide data for the whole ROI by multiplying with the total planted area for that given year and state in order to obtain an effective "planted area". We compare this number for every year against the integrated (or cumulative) SIF radiances (monthly ROI averages) from April onwards to June.

\begin{figure}[htbp]
\centering
\includegraphics{../corn_soy_planted_sif_18.pdf}
\caption{Crop planting progress (1 acre $\approx 4047$ m$^2$) at week 18 as a function of time-integrated monthly SIF radiances from February to June. Uncertainty bars for SIF is the standard error on the 6 different SIF time series. Low values for the years $2013$ and $2014$ are the result of planting delays due to rainfall and cold temperatures (see Section \ref{sec:SIF_TS}). The values in the brackets within the regression equation (above plots) is the uncertainty of the fitted slope and offset.}
\label{fig:corn_soy_planted_sif}
\end{figure}

The result for both corn and soybeans is shown in Figure~\ref{fig:corn_soy_planted_sif}. It shows that the time-integrated SIF radiances correspond very well to the crop planting progress of that given year at the first week of May (week 18). Week 18 was chosen as a reference point as it is generally in the first half of the planting season, which usually starts in early April, or week 14. \citet{grassini2011high} state the mean planting date (or sowing date) at day 117 of the year (last week of April) for the years 2005 to 2007 for their study in Nebraska. Between 2010 and 2016, planting progress has reached close to $100\%$ by week 23 (beginning of June) according to USDA surveys, and no planting has been done after week 26. Before week 17, the variability of planting is too high between nine states and the ROI-averaged SIF is therefore not representative of the Corn Belt as a whole. Table~\ref{tbl:planting_progress_table} shows the correlation coefficients of the relationships between SIF and planting progress (as in Figure~\ref{fig:corn_soy_planted_sif}) along with the coefficient of variation (COV) of the planting progress of the given week, averaged over the 7 years.

\begin{table}[htp]
\begin{center}
\begin{tabular}{r|c|c|c|c}
Week Nr. & COV Corn & COV Soybeans & Corn & Soybeans \\
\hline
16 & 1.04 & 1.37 & $r = 0.59$ & $r = 0.27$ \\
17 & 0.80 & 1.06 & $r = 0.60$ & $r = 0.51$ \\
18 & 0.48 & 0.96 & $r = 0.78$ & $r = 0.71$ \\
19 & 0.31 & 0.61 & $r = 0.56$ & $r = 0.65$ \\
20 & 0.18 & 0.45 & $r = 0.78$ & $r = 0.65$ \\
%21 & 0.09 & 0.30 &            &            \\
%22 & 0.05 & 0.21 &            &            \\
\end{tabular}
\end{center}
\label{tbl:planting_progress_table}
\caption{Relationship between cumulative SIF (Apr-Jun) and planting progress for different weeks of the year, each row representing the same analysis as in Figure~\ref{fig:corn_soy_planted_sif}.}
\end{table}%

The SIF radiances do not only reflect the crop status during the growing season. Also the total corn and soybean yield for the entire year has an apparent linear relationship with the cumulative SIF radiances from July until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}. The record-low yield due to the 2012 drought is highly apparent in the figure, also making it clear that a yield prognosis based on planting progress alone (Fig.~\ref{fig:corn_soy_planted_sif}) is not feasible.

\begin{figure}[htbp]
\centering
\includegraphics{../corn_soy_yield_sif.pdf}
\caption{Annual crop yield (1 bushel corn $\approx 25.4$ kg, 1 bushel soybean $\approx 27.2$ kg) from June to October as a function of the time-integrated monthly SIF radiances from July to October. The uncertainty bars for crop yield is the standard error of all nine states within the ROI, however that number is not taken into account for the linear regression.}
\label{fig:corn_soy_yield_sif}
\end{figure}

The observed good relationship between cumulative SIF, and crop planting and crop yield is not particularly surprising, given the already moderate correlation between the SIF and NDVI/EVI time series anomalies ($r > 0.4$, see Appendix Figure~\ref{fig:anomalies_vi}). The predictive power of hyperspectral indices from remote sensing instruments in characterizing crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010} and \citet{Mkhabela2011}. For the case of the Corn Belt, (monthly cumulative) NDVI/EVI are worse predictors than SIF for planting ($r = 0.59$ / $r = 0.56$ for corn) but slightly better predictors when looking at yield ($r = 0.91$ / $r = 0.87$ for corn). Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.90$ and $r = 0.86$ for corn yield, but are worse for corn planting progress ($r = 0.54$ / $r = 0.51$).
%The better performance of NDVI/EVI as well as LAI and FVC most likely stem from the noisy nature of the SIF data (see Section \ref{sec:GOSAT_SIF}). Even at the scale of the ROI, monthly values of the ROI-averaged SIF can have an attached uncertainty of at least $\approx 20\%$ (estimated through sub-regional aggregation).

@@

The first control is to look at the relationship between total planted area in the nine states against crop yield, where the planted area and yield values are separate for each crop. This is shown in Figure~\ref{fig:corn_soy_yield_TOTAL_PLANTED}. We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative, weak ($r = 0.27$) and statistically insignificant correlation ($p=0.23$). This negative correlation for corn is solely due to the year 2012, removing that one data point reduces the correlation coefficient to $r = 0.00$, which is already hinted by the large p-value of $0.23$. The positive and significant correlation for soybeans is explained through both the steadily increasing yields together with a general increase in soybean planting. The USDA projects soybeans to reach similar levels to corn in terms of amount of planted acres in the near future \citep{USDA-prognosis}. We cannot distinguish whether a specific GOSAT footprint covered a soy field or a corn field (or any other crop) at the time of measurement. Hence we can not completely reject the possibility that the SIF signal we see in Figure~\ref{fig:corn_soy_yield_sif} is due to mainly covering soybean fields. Since most farmers in the Corn Belt practice individual crop rotation between corn and soybeans \citep{suyker2012gross}, it is most likely that we are sampling a mix between corn, soybeans, and to a lesser extent, wheat. We therefore assume that the SIF-yield relationship is not driven due to sampling that is heavily weighted towards soybean fields.

@@

For the third control, we investigate a potential sampling bias. Already shown in Figure~\ref{fig:lc_diff_monthly}, there is a variability in terms of the surfaces sampled by GOSAT, mostly a result of changing cloud cover and sampling strategy. We compare the crop yield to the fraction of cropland (as determined by the ESA CCI LC map) that all GOSAT soundings see in a given year. Here we use the same set of soundings that was pre-filtered beforehand, so only individual soundings are considered that cover more than $50\%$ of the crop type land cover type. The observed correlations at $r < 0.36$ are weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.41$), but neither relationship is statistically significant ($p > 0.15$).

@@

\appendix
\section{Additional Plots}

\begin{figure}[htbp]
\centering
\includegraphics{../anomalies_755_abs_1_median.pdf}
\caption{SIF anomaly compared to the normalized differential vegetation index (NDVI), enhanced vegetation index (EVI), fractional vegetation cover (FVC) and leaf area index anomalies (LAI). Both FVC and LAI reproduce almost the same anomalies as SIF with the main difference being the strength of the positive 2010 anomaly, and LAI not showing any anomaly in 2014 at all. NDVI and EVI show a more extended positive anomaly for the 2011/2012 winter season.}
\label{fig:anomalies_vi}
\end{figure}
